---
title: "MSdev untargeted workflow"
description: >
  End-to-end untargeted LC-MS (lipidomics-style) pipeline: convert,
  xcms processing, spectra extraction, CompoundDb annotation, stats,
  export, and differential figures by sample.type.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSdev untargeted workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette mirrors the current stock untargeted path used in project
records: raw → xcms → spectra → annotation → stats/export → DEP figures
per `sample.type`.

```text
MSdev() / MSdev_load()
    → MSdev_msConvert
    → MSdev_checkSampleInfo
    → MSdev_set_param (CentWave + PeakDensity)
    → MSdev_xcmsProcessing
    → MSdev_extract_Spectra
    → MSdev_annotation (CompoundDb)
    → MSdev_get_Stat → MSdev_export → MSdev_save
    → DEP PCA / TIC / volcano / heatmap by sample.type
```

---

## 1. Create or resume a project

**New project** from a raw-data directory:

```{r}
library(MSdev)

object <- MSdev("path/to/rawDataDir")
```

**Resume** a saved object (skip create + earlier steps already done):

```{r}
object <- MSdev_load("path/to/MSdev_YYYY_MM_DD.Rdata")
```

In practice use one entry point: create for a fresh study, load when
continuing.

---

## 2. Convert and check sample info

```{r}
object <- MSdev_msConvert(object)
object <- MSdev_checkSampleInfo(object)
```

- `MSdev_msConvert()` converts vendor raw files when needed; if inputs are
  already `.mzML` / `.mzXML`, conversion is skipped.
- `MSdev_checkSampleInfo()` validates `sampleInfo` (groups, polarity,
  `msLevels`, `xcmsProcessing`, etc.). Fix metadata interactively if prompted.

---

## 3. Set xcms parameters

Tune peak picking and correspondence before processing (example values from
a recent lipidomics run):

```{r}
object <- MSdev_set_param(
  object,
  findChromPeaks = xcms::CentWaveParam(
    ppm = 25,
    prefilter = c(3, 100),
    peakwidth = c(10, 60),
    snthresh = 10,
    fitgauss = TRUE,
    verboseBetaColumns = TRUE
  ),
  groupChromPeaks = xcms::PeakDensityParam(
    sampleGroups = "A",
    minFraction = 0.5,
    binSize = 0.005,
    bw = 20,
    ppm = 25
  )
)
```

Adjust `ppm`, `peakwidth`, `bw`, and `minFraction` to the instrument and
chromatography. `sampleGroups` in `PeakDensityParam` is a placeholder here;
`MSdev_xcmsProcessing()` uses the project sample groups when it runs.
CentWave `verboseBetaColumns = TRUE` writes `beta_cor` / `beta_snr` onto
`chromPeaks` during picking. Optional peak-shape filtering:
`MSdev_xcmsProcessing(object, beta_cor_thresh = 0.5)` fills NA scores
with `chromPeakSummary()` after merge (finite CentWave scores are kept), then
keeps peaks with `beta_cor >=` the threshold (remaining `NA` are dropped).
Default `NULL` skips re-calc and filtering.

---

## 4. Feature detection and spectra

```{r}
object <- MSdev_xcmsProcessing(object)
object <- MSdev_extract_Spectra(object)
```

- `MSdev_xcmsProcessing()` runs peak picking / grouping (and related xcms
  steps) into polarity MS1 containers (`PositiveMS1` / `NegativeMS1`).
- `MSdev_extract_Spectra()` loads MS1/MS2 into `@spectra`, assigns `sp_id`,
  and links MS2 to features (`MSdev_assign_MS2`).

---

## 5. Annotation against CompoundDb

Example: LipidBlast SQLite with common lipid adducts and expanded adduct
matching:

```{r}
object <- MSdev_annotation(
  object,
  expand_adduct = TRUE,
  cpdb_path = "path/to/CompoundDB/Lipidblast.sqlite",
  selected_adduct = c(
    "[M]+", "[M+NH4]+", "[M+H]+", "[M+Na]+",
    "[M-H]-", "[M+HCOO]-", "[M+CH3COO]-"
  )
)
```

Point `cpdb_path` at any CompoundDb SQLite used for the study. Change
`selected_adduct` for metabolomics vs lipidomics ion modes.

---

## 6. Stats table, export, and save

```{r}
object <- MSdev_get_Stat(object, score_thresh = 0.3)
MSdev_export(object)
MSdev_save(object)
```

- `score_thresh` filters annotation scores when building the stats /
  metabolite tables.
- `MSdev_export()` writes tabular outputs under the project directory.
- `MSdev_save()` serializes the `MSdev` object for later `MSdev_load()`.

---

## 7. Figures and differential analysis

Downstream plots use a `SummarizedExperiment` from annotated metabolites
and DEP helpers. Outputs go under `projectDir/Statistic/`.

```{r}
library(patchwork)

proj.dir <- object@projectInfo$projectDir
data.se <- get_MSdev_DEP_se(object, from = "metabolite", QC_RSD = Inf)
```

### 7.1 PCA and TIC overview

```{r}
p.pca <- DEP_plot_PCA(data.se)
export_graph2pdf(
  p.pca,
  file.path(proj.dir, "Statistic", "Figures.pdf"),
  width = 3, height = 3
)

p1 <- plot_xcms_TIC(object@xcmsData$PositiveMS1) +
  labs(title = "Positive TIC")
p2 <- plot_xcms_TIC(object@xcmsData$NegativeMS1) +
  labs(title = "Negative TIC")
p <- p1 + p2 + plot_layout(ncol = 1)
export_graph2pdf(
  p,
  file.path(proj.dir, "Statistic", "Figures.pdf"),
  width = 10, height = 8, append = TRUE
)
```

### 7.2 Differential analysis by `sample.type`

For each non-Blank / non-QC `sample.type`, write:

- `Statistic/<type>/Figures.pdf` — volcano (unadjusted then adjusted) + heatmap
- `Statistic/<type>/diff.metabolites.xlsx` — contrast tables

```{r}
sample.types <- unique(as.character(data.se$sample.type))
sample.types <- sample.types[!is.na(sample.types) & nzchar(sample.types)] |>
  setdiff(c("Blank", "QC"))

for (stype in sample.types) {
  out.dir <- file.path(proj.dir, "Statistic", stype)
  dir.create(out.dir, recursive = TRUE, showWarnings = FALSE)
  fig.pdf <- file.path(out.dir, "Figures.pdf")
  diff.xlsx <- file.path(out.dir, "diff.metabolites.xlsx")

  data.se1 <- data.se[, data.se$sample.type == stype]
  data.se.p <- DEP_preprocess(data.se1)

  # volcano without p-adjustment
  data.diff <- DEP_test_diff(data.se.p, type = "all")
  data.diff <- DEP_add_rejections(data.diff, p.adjust = FALSE)
  p.diff <- ggplot_sum_patchwork(DEP_plot_volcano(data.diff, "all"))
  export_graph2pdf(p.diff, fig.pdf, width = 10, height = 10)

  # volcano with p-adjustment + export table
  data.diff <- DEP_test_diff(data.se.p)
  data.diff <- DEP_add_rejections(data.diff, p.adjust = TRUE)
  p.diff <- ggplot_sum_patchwork(DEP_plot_volcano(data.diff, "all"))
  export_graph2pdf(p.diff, fig.pdf, width = 10, height = 10, append = TRUE)
  table.diff <- DEP_get_diff_table(data.diff, contrast = "all", keep.all = TRUE)
  xlsx.write.list(table.diff, diff.xlsx)

  # significant features heatmap
  data.diff <- DEP_test_diff(data.se.p, type = "all")
  data.diff <- DEP_add_rejections(data.diff, p.adjust = FALSE)
  data.hm <- DEP_filter_significant(data.diff)
  hm <- DEP_plot_heatmap(data.hm)
  export_graph2pdf(hm, fig.pdf, width = 10, height = 20, append = TRUE)
}
```

Requires usable `sample.type` (and contrast design) in the DEP
`SummarizedExperiment` column data. Skip or subset types as needed for
exploratory runs (`QC_RSD = Inf` disables QC-RSD filtering in the example).

---

## 8. Optional next steps

| Step | Function | When |
|------|----------|------|
| Feature compounding (xcms-style) | `MSdev_xcms_group_features()` | After xcms, before or with annotation |
| Custom EIC grouping | `MSdev_group_feature_EIC()` | When you need stored EIC similarity matrices |
| Feature chromatograms | `MSdev_get_feature_chrom()` | Before custom EIC grouping / EIC reports |

See also the articles on Spectra backends, chromatogram extraction, and
`EicSimilarityParam` feature grouping.
