---
title: "Get started with MSdev"
description: >
  Overview of the MSdev S4 project object, core slots, preferred accessors,
  and a minimal untargeted LC-MS pipeline.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with MSdev}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

`MSdev` is an LC-MS **project shell**: one S4 object holds sample metadata,
xcms feature results, spectra, annotation, and downstream analysis state.
Chemistry / molecule-graph helpers live in companion package **MSCC**; this
package focuses on processing, annotation glue, and stats/export.

For a full lipidomics-style run (params, CompoundDb annotation, DEP figures),
see the vignette *MSdev untargeted workflow*.

---

## 1. Install and load

```{r}
# remotes::install_github("DrRuiLi/MSdev")
library(MSdev)
```

Bioconductor dependencies such as `xcms`, `Spectra`, and `ProtGenerics` must
be available. Install with `BiocManager::install()` if needed.

---

## 2. The `MSdev` object

Create from a directory of raw files (`.wiff`, `.raw`, `.mzML`, `.mzXML`, …):

```{r}
object <- MSdev(rawDataDir = "path/to/rawDataDir")
# optional: projectDir = "...", experimentInfo = MS_Exp()
```

Resume a saved project:

```{r}
object <- MSdev_load("path/to/MSdev_YYYY_MM_DD.Rdata")
```

| Slot | Role |
|------|------|
| `projectInfo` | Paths, counts, save file name, acquisition summary |
| `processingInfo` | xcms / pipeline parameters |
| `sampleInfo` | Per-file sample table (groups, polarity, msLevels, …) |
| `experimentInfo` | `MS_Exp` experiment metadata |
| `xcmsData` | Polarity MS1 `XcmsExperiment`s (`PositiveMS1` / `NegativeMS1`) and chromatograms |
| `spectra` | On-disk MS1 / MS2 (`sp_id` as `spectraNames`) |
| `annotation` | Compound / MS2 annotation results |
| `advancedAna` | Extra analyses (e.g. EIC similarity matrices) |

---

## 3. Minimal untargeted chain

Stock order used in current project records:

```{r}
object <- MSdev("path/to/rawDataDir")

object <- MSdev_msConvert(object)
object <- MSdev_checkSampleInfo(object)

object <- MSdev_set_param(
  object,
  findChromPeaks = xcms::CentWaveParam(ppm = 25, peakwidth = c(10, 60)),
  groupChromPeaks = xcms::PeakDensityParam(
    sampleGroups = "A", minFraction = 0.5, bw = 20, ppm = 25
  )
)

object <- MSdev_xcmsProcessing(object)
object <- MSdev_extract_Spectra(object)   # stores spectra + assigns MS2 to features

object <- MSdev_annotation(
  object,
  expand_adduct = TRUE,
  cpdb_path = "path/to/CompoundDb.sqlite"
)

object <- MSdev_get_Stat(object, score_thresh = 0.3)
MSdev_export(object)
MSdev_save(object)
```

Optional after features exist:

```{r}
object <- MSdev_xcms_group_features(object)  # RT → abundance → EIC (xcms-style)
object <- MSdev_group_feature_EIC(object)    # custom EIC similarity + stored matrices
```

---

## 4. Preferred accessors

Prefer helpers over digging in slots:

```{r}
get_MSdev_Spectra(object, msLevel = 2, polarity = 1)
get_MSdev_Chromatogram(object, polarity = 1)
get_MSdev_spectra_target_list(object)
```

MS1 feature containers:

```{r}
object@xcmsData$PositiveMS1
object@xcmsData$NegativeMS1
# spectra on MS1 xcms objects: ProtGenerics::spectra(xcms)
```

Feature–MS2 links use character `sp_id` vectors in
`featureDefinitions$ms2_id`, matched to MS2 `spectraNames`.

---

## 5. Demo data

If bundled demos are available on your machine:

```{r}
msdev.demo <- load_demo("MSdev")
xcms.demo <- load_demo("xcms")       # alias for XcmsExperiment
```

---

## 6. Where to go next

| Topic | Vignette / article |
|-------|--------------------|
| Full untargeted + DEP figures | *MSdev untargeted workflow* |
| Spectra backends | article *Spectra backends* |
| Fast chromatogram extraction | article *xcms chromatogram extraction* |
| Feature grouping / EIC similarity | article *Feature grouping with EicSimilarityParam* |
| Formula candidates (Rdisop) | article *Rdisop mass decomposition* |

Related packages: **MSCC** (chemistry / graphs), **xcms**, **Spectra**.
