---
title: "MSIP_Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSIP_Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


This vignette documents the core **data structures** used by the MSdev package for:

-   the `MSdev` *project container* object (MS data processing + analysis state)
-   the MSIP *isotopologue/isotopomer* objects (fragment/atom mapping + solving)

# The `MSdev` object

`MSdev` is an S4 class used as a **project-level container** for mass spectrometry workflows (raw data import/convert, xcms processing, spectra extraction, annotation, and downstream statistics).

## Slots (fields)

The class is defined in `R/MSdev-class.R` as:

-   **`projectInfo`** *(list)*: project metadata and paths, including:
    -   `rawDataDir`, `projectDir`, detected `rawDataFormat`
    -   file/sample counts and acquisition summary (MS level, polarity, etc.)
    -   the default path for saving the object (`MSdevFile`)
-   **`processingInfo`** *(list)*: processing parameters and “done” flags, e.g.:
    -   `readInRawData$done` (initialized in the constructor)
    -   `rawDataConvert` (set after conversion)
    -   `MSdevParam` (xcms parameter list used for processing)
-   **`sampleInfo`** *(data.frame)*: sample/file table derived from filenames and mzR metadata:
    -   sample names/types (Sample/QC/Blank, etc.), polarity, file paths
    -   acquisition tags such as `scanType` and `xcmsProcessing`
-   **`experimentInfo`** *(`MS_Exp`)*: experiment metadata (e.g., internal standards, gradients) used for defaults.
-   **`xcmsData`** *(list)*: xcms objects and derived products (often keyed by polarity, e.g. `PositiveMS1`, `NegativeMS1`).
-   **`spectra`** *(list)*: MS1/MS2 spectra objects (often stored as on-disk `.rds` via helpers).
-   **`annotation`** *(list)*: annotation intermediates and results (database paths, candidates, scores, etc.).
-   **`advancedAna`** *(list)*: analysis-ready objects/tables (e.g. `SummarizedExperiment` outputs like `feature.se`, `metabolite.se`).

## Typical lifecycle

The workflow in `R/MSdev-workflow.R` shows a typical pipeline:

1.  Create: `MSdev(rawDataDir, projectDir, experimentInfo)`
2.  (Optional) Convert raw → mzML: `MSdev_msConvert()`
3.  xcms processing: `MSdev_xcmsProcessing()`
4.  Extract spectra + match MS2 to features: `MSdev_extract_Spectra()` then `MSdev_match_Spectra_to_feature()`
5.  Annotate: `MSdev_annotation()`
6.  Build stats-ready objects: `MSdev_get_Stat()`

## Inspecting an `MSdev` object

```{r, eval = FALSE}
msdev <- MSdev(rawDataDir = "path/to/raw/data")

msdev              # calls the S4 show() method
slotNames(msdev)   # list top-level slots

str(msdev@projectInfo, max.level = 1)
head(msdev@sampleInfo)
names(msdev@xcmsData)
names(msdev@spectra)
names(msdev@annotation)
names(msdev@advancedAna)
```

# MSIP data structures

The MSIP-related classes are a small set of S4 objects focused on:

-   representing **fragment-group ↔ atom** relationships (`MSIPFragmentMap`)
-   bundling spectra + maps + solving results (`MSIPCoreData`)
-   storing solved isotopomer models (`MSIPIsotopomerMap`)
-   metabolite-centric isotopologue bundles (`MSIPMetaboliteData`, `MSIPIsotopologueData`)

## `MSIPFragmentMap`

Defined in `R/MSIPCoreData.R`:

-   **`FG.atom.matrix`** *(matrix)*: fragment-group × atom membership (which atoms belong to which fragment groups).
-   **`FG.ratio.matrix`** *(matrix)*: fragment-group × labeled-state ratios (observed labeling ratios/intensities per fragment group).
-   **`FG.data`** *(data.frame)*: per-fragment-group metadata used by filtering/solving.

The `show()` method prints a short summary like “Map of N fragment group, M atom, K labeled”.

## `MSIPCoreData`

Also in `R/MSIPCoreData.R`, this is the main “working object” during MSIP solving:

-   **`Spectra`** *(ANY)*: spectra backing data (kept flexible; can be a `Spectra` object, list, etc.).
-   **`MSIPFragmentMap`** *(`MSIPFragmentMap`)*: the fragment mapping described above.
-   **`Solve`** *(list)*: cached solver state and results (including parameters used for filtering/solving), e.g.:
    -   isotopomer maps used in inference
    -   natural abundance correction flags/ratios
    -   thresholds used for filtering/solving

`isEmpty(MSIPCoreData)` is defined as `isEmpty(MSIPFragmentMap)` (empty when `nrow(FG.atom.matrix) == 0`).

## `MSIPIsotopomerMap`

Also in `R/MSIPCoreData.R`, this represents the solved isotopomer model:

-   **`isotopomer.defination`** *(matrix)*: isotopomer definitions (label state per atom).
-   **`isotopomer.contribution`** *(matrix)*: how isotopomers contribute to labeled fragments.
-   **`Labeled.FG.data`** *(data.frame)*: labeled fragment data used for solving.
-   **`isotopomer.probability`** *(numeric)*: inferred isotopomer probabilities.
-   **`solve`** *(list)*: additional solver details/metadata.

## `MSIPIsotopologueData` and `MSIPMetaboliteData`

Defined in `R/MSIP-class.R`:

-   **`MSIPIsotopologueData`** *(contains `list`)*: a list-like container of isotopologues, typically keyed by names containing `"M"` (e.g. `M+0`, `M+1`, ...). Its `show()` prints how many isotopologues and their formatted names.

-   **`MSIPMetaboliteData`**: a metabolite-centric container with:

    -   **`CompoundInfo`** *(list)*: compound metadata
    -   **`Spectra`** *(list)*: spectra associated with the metabolite
    -   **`MSIPIsotopologueDatas`** *(`MSIPIsotopologueData`)*: isotopologue bundle for that metabolite

## Inspecting MSIP objects

```{r, eval = FALSE}
# Given an MSIPCoreData object (example name: core)
slotNames(core)
core@FG_map
str(core@solve, max.level = 1)

# Given an MSIPIsotopomerMap object (example name: isoMap)
slotNames(isoMap)
isoMap

# Given an MSIPMetaboliteData object (example name: m)
slotNames(m)
names(m@MSIPIsotopologueDatas)
```


# **Workflow**

## Untargeted analysis

An untargeted MSIP analysis generally include such steps:

1. MS1 full scan or DDA analysis
2. Screen isotopologues
3. Targeted MS2 acquisition for isotopologues
4. MSIP analysis

### 1. MS1 full scan or DDA analysis

### 2. Screen isotopologues

## Targeted analysis

The targeted MSIP workflow is designed for compounds with known identity (formula, SMILES, RT) and involves the following steps:

### Step 1: Import Compound Table

Prepare a compound table with the following required columns:
- `compound_id`: Unique identifier for each compound
- `name`: Human-readable compound name
- `formula`: Molecular formula (e.g., "C6H12O6")
- `smiles`: SMILES string for structure representation
- `rt`: Retention time (in seconds)

```{r, eval=FALSE}
# Import compound table from CSV
object <- MSIP_import_compound_table(object, table.path = "path/to/compound_table.csv")
```

### Step 2: Find Isotopologues from Compound Table

For each compound in the table, calculate the m/z of all possible isotopologues (based on the target isotope element, default [13]C) and their adducts (M+H and M-H).

```{r, eval=FALSE}
# Find isotopologues for compounds in the table
object <- MSIP_find_isotopologue_from_compound_table(object)
```

This function:
- Calculates the base m/z for each compound with M+H and M-H adducts
- Generates isotopologue m/z grid based on the maximum number of target atoms
- Stores results in `object@advancedAna$MSIP$isotopologues_table`

### Step 3: Export Acquisition List (Optional)

Generate an acquisition list for targeted MS2 acquisition of the identified isotopologues.

```{r, eval=FALSE}
# Export acquisition list for targeted MS2
MSIP_export_isotopologues_acquisition_list(object)
```

This creates a list of:
- Precursor m/z values for each isotopologue
- Collision energies for fragmentation
- Retention time windows

### Step 4: Perform Targeted MS2 Acquisition

Using the acquisition list, perform targeted MS2 acquisition on a QTRAP or similar instrument. This step is experimental and generates MS2 spectra for each isotopologue at specified collision energies.

### Step 5: Extract MS2 Spectra

After MS2 acquisition, extract and organize the spectra data.

```{r, eval=FALSE}
# Extract MS2 spectra and link to samples
object <- MSdev_extract_Spectra(object)

# Match MS2 spectra to features
object <- MSdev_match_Spectra_to_feature(object)

# Assign MS2 spectra to isotopologues
object <- MSIP_assign_MS2(object, rt.tol = 10)
```

Key functions:
- `MSdev_extract_Spectra()`: Loads MS2 spectra into `object@spectra$MS2_Spectra`
- `MSdev_match_Spectra_to_feature()`: Links MS2 spectra to MS1 features
- `MSIP_assign_MS2()`: Assigns MS2 spectra to isotopologues based on m/z and RT matching

### Step 6: Get CFM Annotation

Generate CFM (Cognitive-Focused Metabolomics) annotations for each compound.

```{r, eval=FALSE}
# Get CFM annotation for compounds
object <- MSIP_get_isotopologues_CFM_annotation(object)
```

This function:
- Uses `get_CFM_data_from_smiles()` to generate predicted fragment spectra
- Creates fragment-to-atom mappings with isotope labeling
- Caches results in a temporary directory for reuse

### Step 7: Build Compound Database (Optional)

If working with a custom compound database.

```{r, eval=FALSE}
# Build compound database
object <- MSIP_build_compoundDB(cpdb = CompDb("path/to/CompDb"))
```

### Step 8: Get Isotopomer Data (Main MSIP Analysis)

This is the core MSIP function that performs the complete isotopomer analysis pipeline.

```{r, eval=FALSE}
# Run MSIP isotopomer analysis (targeted mode)
object <- MSIP_get_isotopomer_data(
  object,
  mode = "targeted",
  iso_ele = "[13]C",
  ppm = 10,
  rt.tol = 10,
  int_thresh = 10^3.8,
  certainty_thresh = 0.6,
  iso_count_max = 30
)
```

#### Workflow Details of `MSIP_get_isotopomer_data`

**For each compound in the compound_table:**

1. **Calculate isotopologue m/z values**
   - Get base m/z for M+H and M-H adducts using `MSCC::chemform_adduct()`
   - Calculate maximum isotopologue count based on target element (e.g., number of carbon atoms)
   - Build isotopologue m/z grid using `MSCC::get_isotope_mass_diff()`

2. **Match MS2 spectra by m/z and RT**
   - Filter MS2 spectra by polarity (positive/negative)
   - Match isotopologue m/z values to spectra using `match_mz_rt()`
   - Uses `isolationWindowTargetMz` and `rtime()` accessors

3. **Separate spectra by isotopologue and sample.source**
   - Group matched spectra by isotopologue form (e.g., [13]C0, [13]C1, [13]C2)
   - Split further by sample source
   - Track polarity for each spectrum group

4. **Construct CFM data**
   - Call `get_CFM_data_from_smiles()` to generate predicted fragments
   - Creates atom mapping with isotope labels
   - Results cached in temp directory

5. **Construct and solve MSIPCoreData**
   - For each isotopologue × sample combination:
     - Filter spectra by polarity
     - Construct MSIPCoreData using `get_MSIPCoreData()`
     - Solve using `MSIPCore_solve()` with specified thresholds
   - Merge positive and negative polarity results via `MSIPCore_merge()`

6. **Store results**
   - Results stored in `object@advancedAna$MSIP$isotopomer_data`
   - Structure: named list of compounds, where each element name is `compound_id`
     and each element value is the `MSIPCoreData_matrix` (rows = isotopologues, cols = sample sources).

### Step 9: Solve Isotopologues (Alternative Entry Point)

If you have pre-processed isotopologue data and want to solve separately.

```{r, eval=FALSE}
# Solve isotopologues with specific parameters
object <- MSIP_solve_isotopologues(
  object,
  int_thresh = 10^3.8,
  certainty_thresh = 0.6,
  ppm = 20,
  timeout = 60
)
```

### Step 10: Get Molecule igraph

Generate molecular graphs for visualization of isotopomer distributions.

```{r, eval=FALSE}
# Get molecule igraphs for isotopomer visualization
object <- MSIP_get_Molecule_igraph(object, fraction_thresh = 0.001)
```

Results stored in `object@advancedAna$MSIP$isotopomer_Molecule_igraph`.

### Step 11: Export Results

Export isotopologues table and analysis results.

```{r, eval=FALSE}
# Export isotopologues table
MSIP_export_isotopologues_table(object)

# Export acquisition list
MSIP_export_isotopologues_acquisition_list(object)
```

### Summary of Key Data Structures

After targeted MSIP analysis, the main results are stored in:

| Slot | Content |
|------|---------|
| `object@advancedAna$MSIP$compound_table` | Input compound table |
| `object@advancedAna$MSIP$isotopomer_data` | Solved isotopomer data (MSIPCoreData matrices) |
| `object@advancedAna$MSIP$isotopomer_Molecule_igraph` | Molecular graphs for visualization |
| `object@projectInfo$MSIP_cfmd_tempdir` | Cached CFM data directory |

### Function Dependency Chain

```
MSIP_import_compound_table
    ↓
MSIP_find_isotopologue_from_compound_table
    ↓
MSIP_get_isotopologues_CFM_annotation
    ↓
MSIP_get_isotopomer_data (targeted mode)
    ↓
MSIP_get_Molecule_igraph (optional visualization)
```



# At-a-glance relationship map

``` text
MSdev
  ├─ projectInfo / processingInfo / sampleInfo / experimentInfo
  ├─ xcmsData  -> processed features (by polarity/acquisition)
  ├─ spectra   -> MS1/MS2 spectra + feature links
  ├─ annotation
  └─ advancedAna -> analysis-ready objects (e.g. SummarizedExperiment)

MSIPCoreData
  ├─ Spectra
  ├─ MSIPFragmentMap (MSIPFragmentMap: FG.atom.matrix / FG.ratio.matrix / FG.data)
  └─ Solve (list; may include MSIPIsotopomerMap + probabilities + parameters)

MSIPMetaboliteData
  ├─ CompoundInfo
  ├─ Spectra
  └─ MSIPIsotopologueDatas (MSIPIsotopologueData; list-like)
```
