---
title: "MSIP_note"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSIP_note}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette documents the core **data structures** used by the MSdev package for:

-   the `MSdev` *project container* object (MS data processing + analysis state)
-   the MSIP *isotopologue/isotopomer* objects (fragment/atom mapping + solving)

## The `MSdev` object

`MSdev` is an S4 class used as a **project-level container** for mass spectrometry workflows (raw data import/convert, xcms processing, spectra extraction, annotation, and downstream statistics).

### Slots (fields)

The class is defined in `R/MSdev-class.R` as:

-   **`projectInfo`** *(list)*: project metadata and paths, including:
    -   `rawDataDir`, `projectDir`, detected `rawDataFormat`
    -   file/sample counts and acquisition summary (MS level, polarity, etc.)
    -   the default path for saving the object (`MSdevFile`)
-   **`processingInfo`** *(list)*: processing parameters and “done” flags, e.g.:
    -   `readInRawData$done` (initialized in the constructor)
    -   `rawDataConvert` (set after conversion)
    -   `MSdevParam` (xcms parameter list used for processing)
-   **`sampleInfo`** *(data.frame)*: sample/file table derived from filenames and mzR metadata:
    -   sample names/types (Sample/QC/Blank, etc.), polarity, file paths
    -   acquisition tags such as `scanType` and `xcmsProcessing`
-   **`experimentInfo`** *(`MS_Exp`)*: experiment metadata (e.g., internal standards, gradients) used for defaults.
-   **`xcmsData`** *(list)*: xcms objects and derived products (often keyed by polarity, e.g. `PositiveMS1`, `NegativeMS1`).
-   **`spectra`** *(list)*: MS1/MS2 spectra objects (often stored as on-disk `.rds` via helpers).
-   **`annotation`** *(list)*: annotation intermediates and results (database paths, candidates, scores, etc.).
-   **`advancedAna`** *(list)*: analysis-ready objects/tables (e.g. `SummarizedExperiment` outputs like `feature.se`, `metabolite.se`).

### Typical lifecycle

The workflow in `R/MSdev-workflow.R` shows a typical pipeline:

1.  Create: `MSdev(rawDataDir, projectDir, experimentInfo)`
2.  (Optional) Convert raw → mzML: `MSdev_msConvert()`
3.  xcms processing: `MSdev_xcmsProcessing()`
4.  Extract spectra + match MS2 to features: `MSdev_extract_Spectra()` then `MSdev_match_Spectra_to_feature()`
5.  Annotate: `MSdev_annotation()`
6.  Build stats-ready objects: `MSdev_get_Stat()`

### Inspecting an `MSdev` object

```{r, eval = FALSE}
msdev <- MSdev(rawDataDir = "path/to/raw/data")

msdev              # calls the S4 show() method
slotNames(msdev)   # list top-level slots

str(msdev@projectInfo, max.level = 1)
head(msdev@sampleInfo)
names(msdev@xcmsData)
names(msdev@spectra)
names(msdev@annotation)
names(msdev@advancedAna)
```

## MSIP (isotope labeling) data structures

The MSIP-related classes are a small set of S4 objects focused on:

-   representing **fragment-group ↔ atom** relationships (`MSIPFragmentMap`)
-   bundling spectra + maps + solving results (`MSIPCoreData`)
-   storing solved isotopomer models (`MSIPIsotopomerMap`)
-   metabolite-centric isotopologue bundles (`MSIPMetaboliteData`, `MSIPIsotopologueData`)

### `MSIPFragmentMap`

Defined in `R/MSIPCoreData.R`:

-   **`FG.atom.matrix`** *(matrix)*: fragment-group × atom membership (which atoms belong to which fragment groups).
-   **`FG.ratio.matrix`** *(matrix)*: fragment-group × labeled-state ratios (observed labeling ratios/intensities per fragment group).
-   **`FG.data`** *(data.frame)*: per-fragment-group metadata used by filtering/solving.

The `show()` method prints a short summary like “Map of N fragment group, M atom, K labeled”.

### `MSIPCoreData`

Also in `R/MSIPCoreData.R`, this is the main “working object” during MSIP solving:

-   **`Spectra_data`** *(ANY)*: spectra backing data (kept flexible; can be a `Spectra` object, list, etc.).
-   **`FG_map`** *(`MSIPFragmentMap`)*: the fragment mapping described above.
-   **`solve`** *(list)*: cached solver state and results, e.g.:
    -   isotopomer maps used in inference
    -   natural abundance correction flags/ratios
    -   thresholds used for filtering/solving

`isEmpty(MSIPCoreData)` is defined as `isEmpty(FG_map)` (empty when `nrow(FG.atom.matrix) == 0`).

### `MSIPIsotopomerMap`

Also in `R/MSIPCoreData.R`, this represents the solved isotopomer model:

-   **`isotopomer.defination`** *(matrix)*: isotopomer definitions (label state per atom).
-   **`isotopomer.contribution`** *(matrix)*: how isotopomers contribute to labeled fragments.
-   **`Labeled.FG.data`** *(data.frame)*: labeled fragment data used for solving.
-   **`isotopomer.probability`** *(numeric)*: inferred isotopomer probabilities.
-   **`solve`** *(list)*: additional solver details/metadata.

### `MSIPIsotopologueData` and `MSIPMetaboliteData`

Defined in `R/MSIP-class.R`:

-   **`MSIPIsotopologueData`** *(contains `list`)*: a list-like container of isotopologues, typically keyed by names containing `"M"` (e.g. `M+0`, `M+1`, ...). Its `show()` prints how many isotopologues and their formatted names.

-   **`MSIPMetaboliteData`**: a metabolite-centric container with:

    -   **`CompoundInfo`** *(list)*: compound metadata
    -   **`Spectra`** *(list)*: spectra associated with the metabolite
    -   **`MSIPIsotopologueDatas`** *(`MSIPIsotopologueData`)*: isotopologue bundle for that metabolite

### Inspecting MSIP objects

```{r, eval = FALSE}
# Given an MSIPCoreData object (example name: core)
slotNames(core)
core@FG_map
str(core@solve, max.level = 1)

# Given an MSIPIsotopomerMap object (example name: isoMap)
slotNames(isoMap)
isoMap

# Given an MSIPMetaboliteData object (example name: m)
slotNames(m)
names(m@MSIPIsotopologueDatas)
```

## At-a-glance relationship map

``` text
MSdev
  ├─ projectInfo / processingInfo / sampleInfo / experimentInfo
  ├─ xcmsData  -> processed features (by polarity/acquisition)
  ├─ spectra   -> MS1/MS2 spectra + feature links
  ├─ annotation
  └─ advancedAna -> analysis-ready objects (e.g. SummarizedExperiment)

MSIPCoreData
  ├─ Spectra_data
  ├─ FG_map (MSIPFragmentMap: FG.atom.matrix / FG.ratio.matrix / FG.data)
  └─ solve (list; may include MSIPIsotopomerMap + probabilities)

MSIPMetaboliteData
  ├─ CompoundInfo
  ├─ Spectra
  └─ MSIPIsotopologueDatas (MSIPIsotopologueData; list-like)
```
