---
title: "Project_record"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project_record}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MSdev)
```

## Sat Jan 13 10:43:20 2024

### DCX Metabolomics

```{r, eval=FALSE}
{
  msdev.dcx <- MSdev("d:/2024_01_08-Duchenxi/Data/")
  msdev.dcx <- load_as_var("d:/2024_01_08-Duchenxi/MSdev_2024_01_13.Rdata")
  msdev.dcx <- MSdev_msConvert(msdev.dcx)
  msdev.dcx <- MSdev_checkSampleInfo(msdev.dcx)
  msdev.dcx <- MSdev_xcmsProcessing(msdev.dcx)
  msdev.dcx <- MSdev_extract_Spectra(msdev.dcx)
  msdev.dcx <- MSdev_match_Spectra_to_feature(msdev.dcx)
  msdev.dcx <- MSdev_annotation(msdev.dcx,
                                expand_adduct= T,
                                cpdb_path = "C:/Users/91879/OneDrive/Code/R/data/MSDB/CompoundDB/CompoundDB.sqlite")
  msdev.dcx <- MSdev_get_Stat(msdev.dcx,QC_RSD = Inf)
  MSdev_save(msdev.dcx)
  MSdev_export(msdev.dcx)


}
```

## Sun Jan 14 12:31:01 2024

### WYQ

```{r, eval=FALSE}
{
  msdev.wyq <- MSdev("d:/WYQ/2024_01_10-Wangyongqiang/Data/")
  msdev.wyq <- MSdev_msConvert(msdev.wyq)
  msdev.wyq <- MSdev_checkSampleInfo(msdev.wyq)
  msdev.wyq <- MSdev_xcmsProcessing(msdev.wyq)
  msdev.wyq <- MSdev_extract_Spectra(msdev.wyq)
  msdev.wyq <- MSdev_match_Spectra_to_feature(msdev.wyq)
  msdev.wyq <- MSdev_annotation(msdev.wyq,
                                expand_adduct= T,
                                selected_adduct = c("[M-H]-",
                                                    "[M-H2O-H]-",
                                                    "[2M-H]-" ,
                                                    "[M+FA-H]-" ,
                                                    "[M+H]+" ,
                                                    "[M-H2O+H]+",
                                                    "[M+NH4]+"
                                ) ,
                                db.path = "C:/Users/91879/OneDrive/Code/R/data/MSDB/SpectraDB/HMDB_KEGG_export_human_pathway.rda")
  msdev.wyq <- MSdev_get_Stat(msdev.wyq)
  MSdev_save(msdev.wyq)
  MSdev_export(msdev.wyq)




}
```

### STAT

```{r, eval=FALSE}
  {
    msdev.wyq <- load_as_var("d:/WYQ/2024_01_10-Wangyongqiang/MSdev_2024_01_14.Rdata")
    msdev.wyq <- MSdev_checkSampleInfo(msdev.wyq)
    msdev.wyq <- MSdev_update_xcms_pdata(msdev.wyq)
    {

      proj.dir <- msdev.wyq@projectInfo$projectDir
      data.se <- get_MSdev_DEP_se(msdev.wyq,from = "metabolite")
      data.se$condition <- data.se$group <- data.se$condition%>%
        gsub(pattern = "_",replacement = "")
      p.pca <- DEP_plot_PCA(data.se)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5)


    }

  }
```

### Sample_P

```{r, eval=FALSE}
      data.se.Sample_P <- DEP_normalization(data.se)
      data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample_P"]
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      rowData(data.diff)$kegg.id <- rowData(data.diff)$kegg_id
      diff.path <- DEP_pathway_enrich(data.diff,
                                      contrast = "all")
      p.diff.path <- lapply(diff.path,
                  plotPathwayEnrichment)%>%
        ggplot_sum_patchwork()+
        plot_layout(ncol = 2)
      export_graph2pdf(p.diff.path , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 15,append = T)
      xlsx.write.list(diff.path,
                      paste0(proj.dir,"/Statistic/Pathway.enrich.xlsx"))
```

### Sample_P

```{r, eval=FALSE}
      data.se.Sample_P <- DEP_normalization(data.se)
      data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample_ACNH"]
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites2.xlsx")
      )

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      rowData(data.diff)$kegg.id <- rowData(data.diff)$kegg_id
      diff.path <- DEP_pathway_enrich(data.diff,
                                      contrast = "all")
      p.diff.path <- lapply(diff.path,
                            plotPathwayEnrichment)%>%
        ggplot_sum_patchwork()+
        plot_layout(ncol = 2)
      export_graph2pdf(p.diff.path , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 15,append = T)
      xlsx.write.list(diff.path,
                      paste0(proj.dir,"/Statistic/Pathway.enrich2.xlsx"))
```

### WYQ

```{r, eval=FALSE}
{
  msdev.wyq <- MSdev("d:/WYQ/2024_01_11-Wangyongqiang/Data/")
  msdev.wyq <- MSdev_msConvert(msdev.wyq)
  msdev.wyq <- MSdev_checkSampleInfo(msdev.wyq)
  msdev.wyq <- MSdev_xcmsProcessing(msdev.wyq)
  msdev.wyq <- MSdev_extract_Spectra(msdev.wyq)
  msdev.wyq <- MSdev_match_Spectra_to_feature(msdev.wyq)
  msdev.wyq <- MSdev_annotation(msdev.wyq,
                                db.path = "C:/Users/91879/OneDrive/Code/R/data/MSDB/SpectraDB/LipidBlast_export.rda")
  msdev.wyq <- MSdev_get_Stat(msdev.wyq, QC_RSD = Inf)
  MSdev_save(msdev.wyq)
  MSdev_export(msdev.wyq)





}
```

### STAT

```{r, eval=FALSE}
  {
    msdev.wyq <- load_as_var("d:/WYQ/2024_01_11-Wangyongqiang/MSdev_2024_01_23.Rdata")
    msdev.wyq <- MSdev_checkSampleInfo(msdev.wyq)
    msdev.wyq <- MSdev_update_xcms_pdata(msdev.wyq)
    msdev.wyq <- MSdev_get_Stat(msdev.wyq)
    {

      proj.dir <- msdev.wyq@projectInfo$projectDir
      data.se <- get_MSdev_DEP_se(msdev.wyq,from = "metabolite")
      data.se$condition <- data.se$group <- data.se$condition%>%
        gsub(pattern = "_",replacement = "")
      p.pca <- DEP_plot_PCA(data.se)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5)


    }

  }
```

### sample_p

```{r, eval=FALSE}
      data.se.Sample_P <- DEP_normalization(data.se)
      data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample_P"]
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 30,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 30,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )
```

### sample_p

```{r, eval=FALSE}
      data.se.Sample_P <- DEP_normalization(data.se)
      data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample_A"]
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 30,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 30,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )
```

### 2024.3.11 HGH lipidomic

```{r, eval=FALSE}
{
  msdev.hgh  <- MSdev("D:/2024_03_07-HGH/Data/")
  msdev.hgh <- load_as_var("d:/2024_03_07-HGH/MSdev_2024_03_11.Rdata")
  msdev.hgh <- MSdev_msConvert(msdev.hgh)
  msdev.hgh <- MSdev_checkSampleInfo(msdev.hgh)
  msdev.hgh <- MSdev_xcmsProcessing(msdev.hgh)
  msdev.hgh <- MSdev_extract_Spectra(msdev.hgh)
  msdev.hgh <- MSdev_match_Spectra_to_feature(msdev.hgh)
  msdev.hgh <- MSdev_annotation(msdev.hgh,cpdb_path = "c:/Users/91879/OneDrive/Code/R/data/MSDB/CompoundDB/Lipidblast3.sqlite",
                                selected_adduct = c("[M]+","[M+NH4]+","[M+H]+","[M+Na]+","[M-H]-","[M+HCOO]-","[M+CH3COO]-"))
  msdev.hgh <- MSdev_get_Stat(msdev.hgh)
  MSdev_export(msdev.hgh)
  MSdev_save(msdev.hgh)

  {

    proj.dir <- msdev.hgh@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.hgh,from = "metabolite")

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5)


  }



}
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

### 2024.3.11 fudan lipidomic

```{r, eval=FALSE}
{
  msdev.fudan  <- MSdev("D:/2024_03_07-Fudan/Data/")
  msdev.fudan <- load_as_var("D:/2024_03_07-Fudan/MSdev_2024_03_11.Rdata")
  msdev.fudan <- MSdev_msConvert(msdev.fudan)
  msdev.fudan <- MSdev_checkSampleInfo(msdev.fudan)
  msdev.fudan <- MSdev_xcmsProcessing(msdev.fudan)
  msdev.fudan <- MSdev_extract_Spectra(msdev.fudan)
  msdev.fudan <- MSdev_match_Spectra_to_feature(msdev.fudan)
  msdev.fudan <- MSdev_annotation(msdev.fudan,cpdb_path = "c:/Users/91879/OneDrive/Code/R/data/MSDB/CompoundDB/Lipidblast3.sqlite",
                                selected_adduct = c("[M]+","[M+NH4]+","[M+H]+","[M+Na]+","[M-H]-","[M+HCOO]-","[M+CH3COO]-"))
  msdev.fudan <- MSdev_get_Stat(msdev.fudan)
  MSdev_export(msdev.fudan)
  MSdev_save(msdev.fudan)

  {

    proj.dir <- msdev.fudan@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.fudan,from = "metabolite")
    #data.se <- data.se[,!colnames(data.se)%in% c( "WT_C1",   "WT_C2" ,  "WT_C3") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5)


  }



}
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Wed Apr 24 13:50:45 2024

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Thu May 23 13:45:06 2024 cx------------------------------

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Fri Jun 7 09:14:22 2024 WYQ------------------------------

### STAT

```{r, eval=FALSE}
  {

      proj.dir <- msdev.wyq@projectInfo$projectDir
      data.se <- get_MSdev_DEP_se(msdev.wyq,from = "metabolite")
      data.replace <- readxl::read_excel("d:/2024_06_04-Wangyongqiang/Statistic/Metabolites2.xlsx",sheet = 2)
      rowData(data.se)$label <- data.replace$name[match(rownames(data.se),
                                                       data.replace$feature_id)]
      data.se$condition <- data.se$group <- data.se$condition%>%
        gsub(pattern = "_",replacement = "")


      data.se  <- data.se[,!data.se$sample.type=="Blank"]




      p.pca <- DEP_plot_PCA(data.se)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5)


    }
```

### Sample_P

```{r, eval=FALSE}
      data.se.Sample_P <- DEP_normalization(data.se)
      data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample"]
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff ,
                       paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 7,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )

      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      rowData(data.diff)$kegg.id <- rowData(data.diff)$kegg_id
      diff.path <- DEP_pathway_enrich(data.diff,
                                      contrast = "all")
      p.diff.path <- lapply(diff.path,
                            plotPathwayEnrichment)%>%
        ggplot_sum_patchwork()+
        plot_layout(ncol = 2)
      export_graph2pdf(p.diff.path , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 15,append = T)
      xlsx.write.list(diff.path,
                      paste0(proj.dir,"/Statistic/Pathway.enrich.xlsx"))


      data.diff$sample.label <- data.diff$ID
      fid <- table.diff$KOF_vs_KOCON%>%
        dplyr::filter(significant)%>%
        dplyr::pull(protein)
      data.plot <- data.diff[fid,]
      rda <- rowData(data.plot)
      cda <- colData(data.plot)
      hm <- assay(data.plot)%>%
        t%>%scale()%>%t

      ComplexHeatmap::Heatmap(
        hm,name = "Z score",
        show_row_names = F,
        show_column_names = F,
        cluster_columns = F,
        column_split = cda$group)
      export::graph2pdf(file = "d:/temp/heatmap.pdf",
                        width = 10,height = 10)
```

## Wed Jun 12 13:50:53 2024 LJW------------------------------

### STAT

```{r, eval=FALSE}
  {

    proj.dir <- msdev.ljw@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.ljw,from = "metabolite")


    data.se  <- data.se[,!data.se$sample.type=="Blank"]




    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5)


  }
```

### Sample_P

```{r, eval=FALSE}
    data.se.Sample_P <- DEP_normalization(data.se)
    data.se.Sample_P <- data.se.Sample_P[,data.se.Sample_P$sample.type== "Sample"]
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 7,append = T)

    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff ,
                     paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 7,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )

    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    rowData(data.diff)$kegg.id <- rowData(data.diff)$kegg_id
    diff.path <- DEP_pathway_enrich(data.diff,
                                    contrast = "all")
    p.diff.path <- lapply(diff.path,
                          plotPathwayEnrichment)%>%
      ggplot_sum_patchwork()+
      plot_layout(ncol = 2)
    export_graph2pdf(p.diff.path , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 15,append = T)
    xlsx.write.list(diff.path,
                    paste0(proj.dir,"/Statistic/Pathway.enrich.xlsx"))
    p.hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(draw(p.hm) ,
                     paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 15,append = T)
```

### Heatmap

```{r, eval=FALSE}
    data.selected <- lapply(1:3,function(x){
      x.df <- readxl::read_excel("d:/LJW_MS data20240611/Statistic/LJW.Labeled.xlsx",
                         sheet = x)
      x.df%>%
        dplyr::mutate(show = as.logical(show))%>%
        dplyr::filter(show)%>%
        dplyr::pull(protein)
    })%>%
      unlist()%>%
      unique()

    data.se <- data.se[data.selected,]
    rda <- rowData(data.se)
    heatmap.matrix <- assay(data.se)%>%t%>%scale%>%t

    Heatmap(heatmap.matrix,
            name = "Z score",
            column_split = data.se$condition,
            cluster_column_slices = F,
            cluster_columns = F,
            show_row_dend = F,
            row_names_side = "left",
            row_labels = rda$label)->p.hm

    export_graph2pdf(draw(p.hm,padding = unit(c(1,8,1,1),"cm")) ,
                     paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 15,height = 15,append = F)
```

## Thu Jun 20 10:20:17 2024 XCH------------------------------

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Wed Jul 31 15:46:54 2024 XCH

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Mon Aug 5 15:51:08 2024 CX

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Sat Aug 10 15:36:57 2024 CX------------------------------

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Mon Aug 12 21:55:13 2024 ZQ------------------------------

### ZQ

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.ZQ@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.ZQ,from = "metabolite")
    data.se <- data.se[,data.se$group%in% c( "G1",   "G2" ,  "G3","G4","QC","Blank") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5)


    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )



  }
```

### ESCC

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.ZQ@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.ZQ,from = "metabolite")
    data.se <- data.se[,data.se$group%in% c( "ESCC_CON",   "ESCC_KO" ,"QC","Blank" ) ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5)


    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )



  }
```

## Wed Jul 31 15:46:54 2024 XCH

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Mon Sep 30 13:49:14 2024

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )
```

## Fri Nov 22 13:08:48 2024 ZJ lipidomic------------------------------

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height =8,append = T)
```

## Wed Dec 4 14:30:02 2024 ZJ lipidomic------------------------------

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height =8,append = T)
```

## Fri Dec 27 12:22:34 2024 ZQ lipidomic------------------------------

### Tumor

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.ZJ@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.ZJ,from = "metabolite")
    data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)


  }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 15,append = T)
```

## Sat Dec 28 14:13:10 2024 ZJ Metabolomics------------------------------

### sample_p

```{r, eval=FALSE}
   # data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 15,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all")
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Sun Feb 9 21:50:46 2025 LE------------------------------

### sample_p

```{r, eval=FALSE}
    # data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 15,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all")
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Tue Feb 11 10:08:20 2025 LE Lipidomics------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- msdev.LE@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.LE,from = "metabolite")
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 120,append = T)
```

## Tue Feb 11 10:08:20 2025 LE Lipidomics 2------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- msdev.LE@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.LE,from = "metabolite")
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 80,append = T)
```

## Tue Feb 11 16:04:38 2025 LE Metabolomics

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p <- plotPathwayEnrichment(data.path[[1]],method = "bubble")
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 4,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Tue Feb 11 16:04:38 2025 LE Metabolomics 2

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p <- plotPathwayEnrichment(data.path[[1]],method = "bubble")
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 4,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Tue Feb 25 23:45:20 2025 LE Metabolomics

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 60,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p <- plotPathwayEnrichment(data.path[[1]],method = "bubble")
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 4,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Wed Feb 26 02:55:00 2025 LE Lipidomics------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- msdev.LE@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.LE,from = "metabolite")
    data.se <- data.se[rowData(data.se)$score>-1,]
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 120,append = T)
```

## Fri Mar 7 20:34:07 2025 Lipidomics------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- msdev.LE@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.LE,from = "metabolite")
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 120,append = T)
```

## Fri Mar 7 20:34:07 2025 LE Lipidomics 2------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- msdev.LE@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(msdev.LE,from = "metabolite")
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 80,append = T)
```

## Fri Mar 7 20:34:07 2025 LE Metabolomics

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Fri Mar 7 20:34:07 2025 LE Metabolomics 2

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Thu Apr 3 14:25:40 2025 CityU NS------------------------------

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.NS@xcmsData$PositiveMS1)+
        labs(titNS = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.NS@xcmsData$NegativeMS1)+
        labs(titNS = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### APC

```{r, eval=FALSE}
    {
      stp <- "APC"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

### HT

```{r, eval=FALSE}
    {
      stp <- "HT"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

### Liver

```{r, eval=FALSE}
    {
      stp <- "Liver"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

### M

```{r, eval=FALSE}
    {
      stp <- "M"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

### P

```{r, eval=FALSE}
    {
      stp <- "P"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

### SCF

```{r, eval=FALSE}
    {
      stp <- "SCF"
      data.se <- get_MSdev_DEP_se(msdev.NS,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(stp)]
      data.se.SampNS_P <- DEP_normalization(data.se)

      p.pca <- DEP_plot_PCA(data.se.SampNS_P)
      export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampNS_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      tabNS.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(tabNS.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",stp,".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampNS_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP.plot.heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 8,height = 8,append = T)
      xlsx.write.list(
        data.path,
        file =paste0(proj.dir,"/Statistic/pathway.",stp,".xlsx")
      )


    }
```

## Thu Jun 5 00:04:30 2025 XHL Metabolomics

### Plot TIC

```{r, eval=FALSE}
    {
     # p1 <- plot_xcms_TIC(msdev.XHL@xcmsData$PositiveMS1)+
     #   labs(titXHL = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.XHL@xcmsData$NegativeMS1)+
        labs(titXHL = "Negative TIC")
      p <- p2+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sampXHL_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.SampXHL_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.SampXHL_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Thu Jun 5 00:04:30 2025 XHL Metabolomics2

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.XHL@xcmsData$PositiveMS1)+
        labs(titXHL = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.XHL@xcmsData$NegativeMS1)+
        labs(titXHL = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sampXHL_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.SampXHL_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.SampXHL_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)

    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title  = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file  =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Thu Jun 19 15:16:10 2025 DDA Mine pos------------------------------

### run after QC FS, once

```{r, eval=FALSE}
  data.dir <- "d:/DDAmine/pos/data/"
  msdev.qe <- MSdev(rawDataDir = data.dir)
  msdev.qe <- MSdev_load("d:/DDAmine/pos/MSdev_2025_06_19.Rdata")
  msdev.qe <- MSdev_msConvert(msdev.qe)
  msdev.qe <- MSdev_xcmsProcessing(msdev.qe)

  msdev.qe@statData <- list()
  msdev.qe <- MSdev_get_Inclusion_Queue(msdev.qe)
```

### run after every time DDA acquired

```{r, eval=FALSE}
  msdev.qe <- MSdev_get_Inclusion_List(msdev.qe)
  msdev.qe <- MSdev_add_sample(msdev.qe,
                               raw.data.dir = "d:/DDAmine/pos/data/")
  msdev.qe <- MSdev_get_MS2acquisitionStat(msdev.qe)

  table(msdev.qe@statData$DDA_mine_queue_Positive$acquired)
```

## Thu Jun 19 15:16:10 2025 DDA Mine neg------------------------------

### run after QC FS, once

```{r, eval=FALSE}
  data.dir <- "d:/DDAmine/neg/data/"
  msdev.qe <- MSdev(rawDataDir = data.dir)
  msdev.qe <- MSdev_load("d:/DDAmine/neg/MSdev_2025_06_19.Rdata")
  msdev.qe <- MSdev_msConvert(msdev.qe)
  msdev.qe <- MSdev_xcmsProcessing(msdev.qe)

  msdev.qe@statData <- list()
  msdev.qe <- MSdev_get_Inclusion_Queue(msdev.qe)
```

### run after every time DDA acquired

```{r, eval=FALSE}
  msdev.qe <- MSdev_get_Inclusion_List(msdev.qe)
  msdev.qe <- MSdev_add_sample(msdev.qe,raw.data.dir = "d:/DDAmine/neg/data/")
  msdev.qe <- MSdev_get_MS2acquisitionStat(msdev.qe)

  table(msdev.qe@statData$DDA_mine_queue_Negative$acquired)
```

## Thu Jun 5 00:04:30 2025 CityUNS Metabolomics2

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.XHL@xcmsData$PositiveMS1,col.group = get_DEP_se_group_color(data.se))+
        labs(titXHL = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.XHL@xcmsData$NegativeMS1,col.group = get_DEP_se_group_color(data.se))+
        labs(titXHL = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### A

```{r, eval=FALSE}
    {


    }
```

### sampXHL_p

```{r, eval=FALSE}
      sample.type = "A"
      data.se <- get_MSdev_DEP_se(msdev.XHL,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(sample.type)]
      proj.dir <- paste0("D:\\20250720.CityUNS/",sample.type)
      dir.create(paste0(proj.dir,"/Statistic"),recursive = T)
      data.se.SampXHL_P <- DEP_preprocess(data.se)
      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampXHL_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff,
                             feature_id = get_DEP_se_sig_feature(data.diff,contrast = "all"))

      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title  = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 10,append = T)
      xlsx.write.list(
        data.path,
        file  =paste0(proj.dir,"/Statistic/pathway.xlsx")
      )
```

### F

```{r, eval=FALSE}
    {


      sample.type = "F"
      data.se <- get_MSdev_DEP_se(msdev.XHL,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(sample.type)]
      proj.dir <- paste0("D:\\20250720.CityUNS/",sample.type)
      dir.create(paste0(proj.dir,"/Statistic"),recursive = T)

      data.se.SampXHL_P <- DEP_preprocess(data.se)
      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampXHL_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff,
                             feature_id = get_DEP_se_sig_feature(data.diff,contrast = "all"))

      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title  = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 10,append = T)
      xlsx.write.list(
        data.path,
        file  =paste0(proj.dir,"/Statistic/pathway.xlsx")
      )
    }
```

### M

```{r, eval=FALSE}
    {


    }
```

### sampXHL_p

```{r, eval=FALSE}
      sample.type = "M"
      data.se <- get_MSdev_DEP_se(msdev.XHL,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(sample.type)]
      proj.dir <- paste0("D:\\20250720.CityUNS/",sample.type)
      dir.create(paste0(proj.dir,"/Statistic"),recursive = T)

      data.se.SampXHL_P <- DEP_preprocess(data.se)
      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampXHL_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff,
                             feature_id = get_DEP_se_sig_feature(data.diff,contrast = "all"))

      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title  = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 10,append = T)
      xlsx.write.list(
        data.path,
        file  =paste0(proj.dir,"/Statistic/pathway.xlsx")
      )
```

### L

```{r, eval=FALSE}
    {



      sample.type = "L"
      data.se <- get_MSdev_DEP_se(msdev.XHL,from = "metabolite")
      data.se <- data.se[,data.se$sample.type%in%c(sample.type)]
      proj.dir <- paste0("D:\\20250720.CityUNS/",sample.type)
      dir.create(paste0(proj.dir,"/Statistic"),recursive = T)


      data.se.SampXHL_P <- DEP_preprocess(data.se)
      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      data.diff <- DEP_test_diff(data.se.SampXHL_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.SampXHL_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff,
                             feature_id = get_DEP_se_sig_feature(data.diff,contrast = "all"))

      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 20,append = T)

      data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
      p.list <- lapply(names(data.path),
                       function(x){
                         p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title  = x)
                       })
      p <- ggplot_sum_patchwork(p.list)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 10,append = T)
      xlsx.write.list(
        data.path,
        file  =paste0(proj.dir,"/Statistic/pathway.xlsx")
      )
    }
```

## Sun Aug 3 15:14:45 2025 Lipidomics------------------------------

### figure

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)
    #data.se <- data.se[,grepl(data.se$group,pattern = "Tumor") ]
    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)




  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 5,height = 5,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff,p.adjust = T)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 80,append = T)
```

## Wed Sep 3 17:17:28 2025 CX Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)





  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_1

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type == "Sample1"]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 80,append = T)

    }
```

### sample_2

```{r, eval=FALSE}
    {
      data.se2 <- data.se[,data.se$sample.type == "Sample2"]
      data.se.Sample_P <- DEP_preprocess(data.se2)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 80,append = T)

    }
```

## Thu Sep 25 15:30:01 2025 Gout OA------------------------------

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","A0")]
    data.se.Sample_P <- DEP_normalization(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP.plot.heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Tue Oct 14 12:56:05 2025 ZWD Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)







  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type == "Sample"]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 5,height = 5,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 6,height = 80,append = T)

    }
```

## Thu Sep 25 15:30:01 2025 ZXY------------------------------

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","BK")]
    data.se.Sample_P <- DEP_preprocess(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP_plot_heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Mon Nov 24 15:10:13 2025 XCH Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)







  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type == "Sample"]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 60,append = T)

    }
```

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)







  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type == "Sample"]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 60,append = T)

    }
```

## Thu Jan 15 11:34:59 2026 CX Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)







  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type == "Sample"]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 60,append = T)

    }
```

## Thu Sep 25 15:30:01 2025 WYQ metabolomic------------------------------

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","BK")]
    data.se.Sample_P <- DEP_preprocess(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP_plot_heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 10,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Thu Sep 25 15:30:01 2025 MHR metabolomic------------------------------

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","BK")]
    data.se.Sample_P <- DEP_preprocess(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP_plot_heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 50,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 20,height = 5,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(msdev.LE@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(msdev.LE@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### sample_p

```{r, eval=FALSE}
    data.se <- data.se[,!data.se$condition%in%c("QC","Blank","BK")]
    data.se.Sample_P <- DEP_preprocess(data.se)
    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    data.diff <- DEP_test_diff(data.se.Sample_P)
    data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

    p.diff.list <- DEP_plot_volcano(data.diff,"all")
    p.diff <- ggplot_sum_patchwork(p.diff.list)
    export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 10,height = 10,append = T)
    table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
    xlsx.write.list(table.diff,
                    paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
    )


    data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
    data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
    #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
    hm <- DEP_plot_heatmap(data.diff)
    export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 6,height = 20,append = T)


    data.path <- DEP_pathway_enrich(data.diff,contrast = "all",method = "GlobalTest")
    p.list <- lapply(names(data.path),
                     function(x){
                       p <- plotPathwayEnrichment(data.path[[x]],method = "bubble",title = x)
                     })
    p <- ggplot_sum_patchwork(p.list)
    export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 8,height = 5,append = T)
    xlsx.write.list(
      data.path,
      file =paste0(proj.dir,"/Statistic/pathway.xlsx")
    )
```

## Mon Mar 2 19:20:34 2026 XCH Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)







  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type %in% c("C","X")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 20,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      hm <- DEP_plot_heatmap(data.diff)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 30,append = T)

    }
```

## Thu Mar 12 10:21:51 2026 XYC Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)






  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se#[,data.se$sample.type %in% c("C","X")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 5,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 5,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
      }

      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("PA","LPA","BRSE","CASE","CE"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }


    }
```

## Thu Apr 9 17:42:33 2026 XYC Lipidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= Inf)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)






  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se#[,data.se$sample.type %in% c("C","X")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
      }

      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("PA","LPA","BRSE","CASE","CE"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }


    }
```

## Wed Jun 10 16:20:03 2026 WSF lpidomics------------------------------

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= 0.3)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)






  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,!data.se$group %in% c("Other","Blank","QC")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      #data.diff <- data.diff[,grepl("LB|V|F",data.diff$group )]
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
      }

      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("PA","LPA","BRSE","CASE","CE"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.se) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.se[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        #ht_opt$TITLE_PADDING = unit(c(4, 4), "points")
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }


    }
```

## Thu Jun 18 2026 Sunjing Lipidomics------------------------------

### processing

```{r, eval=FALSE}
{
  MSdev.obj <- MSdev("D:/data/2026_06_15-sunjing/Data/")
  MSdev.obj <- MSdev_load("d:/data/2026_06_15-sunjing/MSdev_2026_06_18.Rdata")
  MSdev.obj <- MSdev_msConvert(MSdev.obj)
  MSdev.obj <- MSdev_checkSampleInfo(MSdev.obj)
  MSdev.obj <- MSdev_set_param(MSdev.obj,
                               findChromPeaks =
                                 xcms::CentWaveParam(
                                   ppm = 10,
                                   prefilter = c(3,100),
                                   peakwidth = c(10, 60),
                                   snthresh = 10,
                                   fitgauss = T
                                 ),
                               groupChromPeaks =
                                 xcms::PeakDensityParam(
                                   sampleGroups = "A",
                                   minFraction = 0,
                                   binSize = 0.005,
                                   bw = 20,
                                   ppm = 10))
  MSdev.obj <- MSdev_xcmsProcessing(MSdev.obj)
  MSdev.obj <- MSdev_extract_Spectra(MSdev.obj)
  MSdev.obj <- MSdev_annotation(MSdev.obj,
                                expand_adduct= T,
                                cpdb_path = "c:/Users/91879/OneDrive/Code/R/data/MSDB/CompoundDB/Lipidblast.sqlite",
                                selected_adduct = c("[M]+","[M+NH4]+","[M+H]+","[M+Na]+","[M-H]-","[M+HCOO]-","[M+CH3COO]-"))
  MSdev.obj <- MSdev_get_Stat(MSdev.obj,score_thresh = 0.3)
  MSdev_export(MSdev.obj)
  MSdev_save(MSdev.obj)
}
```

### figure SAMPLE1

```{r, eval=FALSE}
  {

    proj.dir <- MSdev.obj@projectInfo$projectDir
    data.se <- get_MSdev_DEP_se(MSdev.obj,from = "metabolite",QC_RSD= NULL)

    p.pca <- DEP_plot_PCA(data.se)
    export_graph2pdf(p.pca , paste0(proj.dir,"/Statistic/Figures.pdf"),
                     width = 3,height = 3)
  }
```

### Plot TIC

```{r, eval=FALSE}
    {
      p1 <- plot_xcms_TIC(MSdev.obj@xcmsData$PositiveMS1)+
        labs(title = "Positive TIC")
      p2 <- plot_xcms_TIC(MSdev.obj@xcmsData$NegativeMS1)+
        labs(title = "Negative TIC")
      p <- p1+p2+plot_layout(ncol = 1)
      export_graph2pdf(p , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 8,append = T)
    }
```

### diff in iwat

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type %in% c("iwat")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",unique(data.se1$sample.type),".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.hm) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.hm[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }

    }
```

### diff in liv

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type %in% c("liv")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",unique(data.se1$sample.type),".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.hm) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.hm[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }

    }
```

### diff in skin

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type %in% c("skin")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",unique(data.se1$sample.type),".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.hm) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.hm[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }

    }
```

### diff in s

```{r, eval=FALSE}
    {
      data.se1 <- data.se[,data.se$sample.type %in% c("s")]
      data.se.Sample_P <- DEP_preprocess(data.se1)
      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      data.diff <- DEP_test_diff(data.se.Sample_P)
      data.diff <- DEP_add_rejections(data.diff,p.adjust = T)

      p.diff.list <- DEP_plot_volcano(data.diff,"all")
      p.diff <- ggplot_sum_patchwork(p.diff.list)
      export_graph2pdf(p.diff , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 20,height = 25,append = T)
      table.diff <- DEP_get_diff_table(data.diff,contrast = "all",keep.all = T)
      xlsx.write.list(table.diff,
                      paste0(proj.dir,"/Statistic/diff.metabolites.",unique(data.se1$sample.type),".xlsx")
      )


      data.diff <- DEP_test_diff(data.se.Sample_P,type = "all")
      data.diff <- DEP_add_rejections(data.diff,p.adjust = F)
      data.hm <- DEP_filter_significant(data.diff)
      hm <- DEP_plot_heatmap(data.hm)
      export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                       width = 10,height = 10,append = T)


      {
        data.hm <- data.se[rowData(data.se)$lipidclass %in% c("DG","TG","PI"),]
        col.info <-SummarizedExperiment::colData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(col_group = condition,
                        column_labels = sample.labels,
                        column_split = group)
        row.info <-SummarizedExperiment::rowData(data.hm)%>%
          as.data.frame()%>%
          dplyr::mutate(row_group = "",
                        row_labels = label)
        rownames(data.hm) <- row.info$name

        heatmap.matrix <-SummarizedExperiment::assay(data.hm[row.info$name,col.info$ID])%>%
          `^`(2,.)%>%t%>%scale%>%t

        rownames(heatmap.matrix) <- row.info$label
        ComplexHeatmap::ht_opt(TITLE_PADDING = unit(c(4, 4), "points"))
        hm <- ComplexHeatmap::Heatmap(
          heatmap.matrix,
          row_split = row.info$lipidclass,
          column_split = col.info$group,
          cluster_columns = F,
          row_names_gp = gpar(fontsize = 6),
          column_title_gp = gpar(fill = get_DEP_se_group_color(data.se),fontsize = 8)
        )
        hm
        export_graph2pdf(hm , paste0(proj.dir,"/Statistic/Figures.pdf"),
                         width = 10,height = 6,append = T)
      }

    }
```
