---
title: "Visualizing xcms data"
description: >
  ggplot2 / patchwork helpers for TICs, peaks, features, chromatograms, and
  XICs from XcmsExperiment, XCMSnExp, and XChromatogram objects.
format: html
# pkgdown GHA has no xcms dataset; do not evaluate examples
execute:
  eval: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

These helpers take an **`XcmsExperiment`** or **`XCMSnExp`** (after peak picking and, for feature plots, correspondence) and return ggplot2, patchwork, or ComplexHeatmap objects. Chromatogram overlays take **`XChromatograms`** / **`XChromatogram`**.

Examples below assume `xcms` is already processed. They are **not evaluated** when pkgdown builds this page (no dataset in CI).

```{r, eval=FALSE}
library(ggplot2)
library(patchwork)

# xcms: XcmsExperiment or XCMSnExp after findChromPeaks / groupChromPeaks
```

```{mermaid}
%%| eval: true
flowchart TD
  xcms["XcmsExperiment or XCMSnExp"]
  chrom["XChromatograms or XChromatogram"]
  qc["Run QC: TIC, MS1 scan frequency"]
  peaks["Peaks: RT-mz map, scan counts, peak EIC"]
  feats["Features: RT-mz map, feature EIC, injection intensity"]
  xic["XIC two-panel"]
  overlay["plot_XChromatograms or mirror"]
  fg["Feature-group EIC or similarity"]
  xcms --> qc
  xcms --> peaks
  xcms --> feats
  xcms --> xic
  xcms --> chrom
  chrom --> overlay
  xcms --> fg
  chrom --> fg
```

---

## 1. Choosing a plotter

| Need | Function | Input class / slots | Returns |
|---|---|---|---|
| MS1 TIC overlay by `pData$group` | `plot_xcms_TIC()` | `XcmsExperiment` / `XCMSnExp` | ggplot |
| MS1 scan frequency vs RT | `plot_xcms_ms1_scan_freq()` | spectra on the xcms object | ggplot |
| All chromPeaks on the RT–m/z plane | `plot_xcms_peaks_distribution()` | `chromPeaks` | ggplot |
| MS1 scans overlapping each peak | `plot_xcms_peaks_ms1_scans()` | `chromPeaks` + spectra | ggplot |
| MS2 scans overlapping each peak | `plot_xcms_peaks_ms2_scans()` | `chromPeaks` + MS2 spectra | ggplot |
| EIC for one chromPeak | `plot_xcms_peaks_Chromatogram()` | `chromPeaks` | ggplot |
| Features on the RT–m/z plane | `plot_xcms_features_distribution()` | `featureDefinitions` | ggplot |
| EIC for one feature (few samples) | `plot_xcms_feature_chromatogram()` | `featureDefinitions` | ggplot |
| Feature intensity vs injection order | `plot_xcms_feature_intensity()` | `featureValues` + `pData` | ggplot |
| Two-panel XIC (EIC + m/z–RT points) | `plot_xcms_xic()` | mz/RT-filtered xcms object | patchwork |
| Overlay chromatogram matrix | `plot_XChromatograms()` | `XChromatograms` / `MChromatograms` | ggplot |
| Tidy chromatogram table | `get_chroms_data()` | `XChromatogram` / `XChromatograms` | data.frame |
| Mirror two traces | `plot_Chromatograph_mirror()` | `XChromatogram` / chromatogram cell | ggplot |
| Pairwise EIC overlay in a feature group | `plot_xcms_feature_group_EIC_comparasion()` | `featureGroups` + EICs | ggplot |
| EIC similarity heatmap | `plot_xcms_feature_group_similarity()` | `otherData$EIC_Similarity` | Heatmap |

---

## 2. Run-level QC

### 2.1 Total ion chromatogram

`plot_xcms_TIC()` plots MS1 TIC traces, one line per file, colored by `Biobase::pData(xcms)$group`. Blank and QC get fixed colors (`grey` / teal); remaining groups use `ggsci::pal_aaas()`. Line alpha shrinks when many files are present.

```{r, eval=FALSE}
plot_xcms_TIC(xcms, title = "TIC")
```

### 2.2 MS1 scan frequency

`plot_xcms_ms1_scan_freq()` bins MS1 scans in successive `rt_window`-wide RT windows (default 5 s) **per file** and plots `scan_count / rt_window`. Use it to check whether the MS1 cycle is stable across the gradient (drops often mark DDA/MS2-heavy regions or source instability).

```{r, eval=FALSE}
plot_xcms_ms1_scan_freq(xcms, rt_window = 5)
```

---

## 3. Chromatographic peaks

These plotters need peak picking (`xcms::chromPeaks`). Subtitles pull CentWave parameters from `processHistory()` (`ppm`, `snthresh`, `prefilter`).

### 3.1 Peak map

`plot_xcms_peaks_distribution()` draws every (non-merged, width < 60 s) peak on RT vs m/z. Color is `log10(maxo)`; `type = "o"` uses point size for peak width, `type = "l"` draws a horizontal segment from `rtmin` to `rtmax`.

```{r, eval=FALSE}
plot_xcms_peaks_distribution(xcms, type = "o")
plot_xcms_peaks_distribution(xcms, type = "l")
```

### 3.2 Scans inside each peak

`plot_xcms_peaks_ms1_scans()` counts MS1 scans whose RT falls in `[rtmin, rtmax]`. A horizontal line at 7 scans is a useful CentWave rule of thumb. With many peaks this can be slow; subset files first.

`plot_xcms_peaks_ms2_scans()` counts MS2 scans whose precursor m/z **and** RT fall in the peak box, and annotates how many peaks have 0–5 MS2 events. The xcms object must still carry MS2 spectra; an MS1-only `XcmsExperiment` cannot produce that overlay.

```{r, eval=FALSE}
plot_xcms_peaks_ms1_scans(xcms)
plot_xcms_peaks_ms2_scans(xcms)
```

### 3.3 Peak EIC

`plot_xcms_peaks_Chromatogram()` extracts one peak’s EIC via `get_xcms_peaks_chromatogram()` and fills the `[rtmin, rtmax]` window.

```{r, eval=FALSE}
pids <- rownames(xcms::chromPeaks(xcms))
plot_xcms_peaks_Chromatogram(xcms, peak_id = pids[[1]], rt = "expand")
```

`rt` is passed through as `rt.range`: `"expand"` (default, ±15 s), `"identity"` (peak box only), or `"all"` (full run). Extraction details: [Fast chromatogram extraction](xcms_chromatogram_extraction.html).

---

## 4. Features

These plotters need correspondence (`xcms::featureDefinitions`).

### 4.1 Feature map

`plot_xcms_features_distribution()` is the feature analogue of the peak map: `rtmed` vs `mzmed`, color = median `maxo`, size = `peakWidth`.

```{r, eval=FALSE}
plot_xcms_features_distribution(xcms)
```

### 4.2 Feature EIC (inspection)

`plot_xcms_feature_chromatogram()` builds a shared mz–RT box from that feature’s `chromPeaks`, extracts chromatograms, and overlays selected samples. If more than five samples are present, it keeps **one sample per `pData$group`** (or the first five if `group` is missing).

```{r, eval=FALSE}
fids <- rownames(xcms::featureDefinitions(xcms))
plot_xcms_feature_chromatogram(xcms, feature.id = fids[[1]])
```

For many features or full-run traces, extract once with `get_xcms_feature_chromatogram()`, then plot with `plot_XChromatograms()` (section 6). The inspection helper still calls `xcms::chromatogram()` internally and is meant for a handful of features.

### 4.3 Intensity along the injection sequence

`plot_xcms_feature_intensity()` plots `featureValues` against injection order. Positive polarity sorts `pData$analysis.time.positive`; negative uses `analysis.time.negative`. Points are colored by `sample.type` (`Blank` / `QC` / `Sample`).

```{r, eval=FALSE}
plot_xcms_feature_intensity(xcms, feature_id_to_show = fids[[1]])
```

---

## 5. Two-panel XIC

`plot_xcms_xic()` is a ggplot2 stand-in for xcms `plot(..., type = "XIC")`:

- **Upper panel:** extracted-ion chromatogram (intensity vs RT)
- **Lower panel:** centroid points (m/z vs RT, colored by intensity)

Supply an **already filtered** `XcmsExperiment` / `XCMSnExp` plus the same mz/RT windows used for filtering (axis limits).

```{r, eval=FALSE}
mzr <- c(760.58, 760.60)
rtr <- c(400, 460)
xcms.filt <- xcms::filterRt(xcms::filterMz(xcms, mz = mzr), rt = rtr)

plot_xcms_xic(
  xcms.filt,
  mzr = mzr,
  rtr = rtr,
  title = "XIC",
  subtitle = sprintf("mz %.4f–%.4f; rt %.0f–%.0f s", mzr[1], mzr[2], rtr[1], rtr[2])
)
```

Set `return.data = TRUE` to get the patchwork plus the chromatogram and point `data.frame`s for custom ggplot layers.

---

## 6. `XChromatogram` / `XChromatograms`

Extraction and plotting are separate. Convert `XChromatograms` / `MChromatograms` / `XChromatogram` to a tidy table with `get_chroms_data()` (columns `rt`, `intensity`, `row`, `col`), or pass the S4 object to `plot_XChromatograms()`.

```{r, eval=FALSE}
chroms <- get_xcms_feature_chromatogram(
  xcms, feature.id = fids[1:8], sample = "all", rt = "expand"
)

plot_XChromatograms(chroms, norm = TRUE, move = TRUE, color_by = "column")
plot_XChromatograms(chroms, norm = FALSE, move = FALSE, color_by = "row")
```

| Argument | Effect |
|---|---|
| `norm = TRUE` | `MSnbase::normalise()` then scale intensities to 0–100 |
| `move = TRUE` | Offset each trace in RT and intensity so overlays do not sit on top of each other |
| `color_by` | `"column"` = sample; `"row"` = feature / region |
| `label_df` | Optional `data.frame(x, y, label)` drawn with `ggrepel` |

`plot_Chromatograph_mirror()` compares two traces (`XChromatogram`, `Chromatogram`, an `XChromatograms` cell, or `data.frame(rt, intensity)`), optionally normalizing each to its own max and flipping the second below zero.

```{r, eval=FALSE}
plot_Chromatograph_mirror(
  chroms[1, 1],
  chroms[2, 1],
  labels = c(fids[[1]], fids[[2]])
)
```

---

## 7. Feature-group EIC views

After feature compounding, `xcms::featureGroups()` labels groups. Pairwise EIC scores (when stored) sit on `MsExperiment::otherData(xcms)$EIC_Similarity`.

```{r, eval=FALSE}
fg <- unique(stats::na.omit(xcms::featureGroups(xcms)))

plot_xcms_feature_group_EIC_comparasion(
  xcms,
  feature_group = fg[[1]],
  expandRt = 2,
  min_width = 20
)

plot_xcms_feature_group_similarity(xcms, order_by = "feature_group")
```

How groups and the similarity matrix are built: [Feature grouping with `EicSimilarityParam`](xcms-feature-group-EicSimilarityParam.html).

---

## 8. Saving figures

Plotters return ggplot / patchwork / Heatmap objects. Save with ggplot2 or the package export helpers:

```{r, eval=FALSE}
p <- plot_xcms_TIC(xcms)
ggplot2::ggsave("TIC.pdf", p, width = 8, height = 4)
open_plot_pdf(p, width = 8, height = 4)
```

---

## 9. Related reading

- [Fast chromatogram extraction](xcms_chromatogram_extraction.html) — `get_xcms_chromatogram`, `get_xcms_peaks_chromatogram`, `get_xcms_feature_chromatogram`
- [Feature grouping with `EicSimilarityParam`](xcms-feature-group-EicSimilarityParam.html)
- Code: `R/dev_xcms.R`, `R/dev_plot.R`
